Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-25 paper.tex
Updates in table colors.

\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\newcommand{\todo}[1]{\color{blue}\xspace[\emph{#1}]\xspace\color{black}}
\newcommand{\note}[2]{\pdfmargincomment[color=yellow,author=#1,open=true]{#2}}
\newcommand{\closednote}[4]{\pdfmargincomment[color=gray,author=#1-#3,open=true]{#1: #2 \textCR \textCR #3: #4}}

@@

\begin{figure*}
\centering
\hspace*{0.2\columnwidth}
\subfloat[Tight integration]{
\def\svgwidth{0.6\columnwidth}
\input{figures/tight.pdf_tex}
\label{archi:tight}
}
\hfill
\subfloat[Service invocation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/service.pdf_tex}
\label{archi:service}
\hspace*{0.2\columnwidth}
}\\
\hspace*{0.2\columnwidth}
\subfloat[Sub-tasking]{
\def\svgwidth{0.6\columnwidth}
\input{figures/sub-task.pdf_tex}
\label{archi:sub-task}
}
\hfill
\subfloat[Pool]{
\def\svgwidth{0.6\columnwidth}
\input{figures/agent.pdf_tex}
\label{archi:agent}
\hspace*{0.2\columnwidth}
}\\
\subfloat[Nested workflows. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-1.pdf_tex}
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-2.pdf_tex}
\label{archi:nested}
}\\
\subfloat[Workflow import. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.5\columnwidth}
\input{figures/import-1.pdf_tex}
\hfill
\def\svgwidth{0.5\columnwidth}
\input{figures/import-2.pdf_tex}
\label{archi:import}
}
\caption{Architectures}
\label{fig:architectures}
\end{figure*}
\begin{table*}
\centering
\footnotesize
\rowcolors{1}{white}{gray!25}
\begin{tabular}{ll}
  \textbf{Architecture} & \textbf{Systems} \\
  \hline
  Tight & \pbox{1.5\columnwidth}{
          Catania Science Gateway Framework~\cite{Ardizzone2012},
          Distributed application runtime environment (DARE~\cite{maddineni2012distributed}),
          DECIDE~\cite{ardizzone2012decide}$^{c,n}$, LONI Pipeline Environment$^n$~\cite{dinov2009efficient}
          }
  \\
  Service & \pbox{1.5\columnwidth}{
            Apache Airvata~\cite{marru2011apache}, e-BioInfra~\cite{shahand2015data}$^{w,n}$, HubZero with Pegasus~\cite{CPE:CPE3257}, MoSGrid~\cite{krüger2014mosgrid}$^w$, System in~\cite{wu2010accelerating}, Vine Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual Imaging Platform~\cite{GLAT-13}$^n$, WS-PGRADE/gUSE framework~\cite{Kacsuk2012},
            Science gateways in ~\cite{kacsuk2014science}$^w$
            } \\
  Sub-task & CBRAIN and PSOM~\cite{GLAT-16}$^n$, CBRAIN and FSL$^n$\\
  Pool & SHIWA pool~\cite{ROGE-13}\\
  Nested & \pbox{1.5\columnwidth}{SHIWA Simulation Platform (Coarse-Grained Interoperability~\cite{terstyanszky2014enabling})$^w$, HubZero with Pegasus (via hierarchical workflows)~\cite{Deelman201517} \todo{others}
  }\\
  Import & SHIWA Simulation Platform (Fine-Grained Interoperability)~\cite{plankensteiner-prodan-etal:2013}$^w$
\end{tabular}
\caption{Classification of science gateways based on the architecture used to integrate workflow engines. $^c$: based on the Catania Science Gateway Framework. $^w$: based on WS-PGRADE/gUSE. $^n$: used for neuroimaging.}
\label{table:system-classification}
\end{table*}

@@

\todo{Add description of a real system}

\todo{Refer to ``From the desktop to the grid: scalable bioinformatics via workflow conversion Luis de la GarzaEmail author, Johannes Veit, Andras Szolek, Marc Röttig, Stephan Aiche, Sandra Gesing, Knut Reinert and Oliver Kohlbacher''}

@@

                                     & \cellcolor[HTML]{99E899}3

@@

                                     & \cellcolor[HTML]{99D199}4
                                     & \cellcolor[HTML]{99BB99}5
                                     & \cellcolor[HTML]{99E899}3\\

@@

                                     & \cellcolor[HTML]{99F399}6

@@

                                     & \cellcolor[HTML]{99E899}7
                                     & \cellcolor[HTML]{99BB99}11
                                     & \cellcolor[HTML]{99E899}7\\

@@

                                     & \cellcolor[HTML]{99EF99}\textbf{9}

@@

                                     & \cellcolor[HTML]{99E099}\textbf{11}
                                     & \cellcolor[HTML]{99BB99}\textbf{16}
                                     & \cellcolor[HTML]{99E899}\textbf{10}\\

@@

                                     & \cellcolor[HTML]{99DD99}1

@@

                                     & \cellcolor[HTML]{99BB99}2
                                     & \cellcolor[HTML]{99BB99}2
                                     & \cellcolor[HTML]{99DD99}1\\
  Specific interactions -- \texttt{R$_2$} & \cellcolor[HTML]{99F199}2
                                     & \cellcolor[HTML]{99E399}3

@@

                                     & \cellcolor[HTML]{99D699}4
                                     & \cellcolor[HTML]{99BB99}6
                                     & \cellcolor[HTML]{99E399}3\\
  \textbf{Total} (execution software pieces)& \cellcolor[HTML]{99F599}\textbf{2}
                                     & \cellcolor[HTML]{99E199}\textbf{4}

@@

                                     & \cellcolor[HTML]{99CE99}\textbf{6}
                                     & \cellcolor[HTML]{99BB99}\textbf{8}
                                     & \cellcolor[HTML]{99E199}\textbf{4}\\

@@

  New engine type -- \texttt{E$_1$}  & \cellcolor[HTML]{99D899}3
                                     & \cellcolor[HTML]{99C499}4
                                     & \cellcolor[HTML]{99EB99}2
                                     & \cellcolor[HTML]{99D899}3
                                     & \cellcolor[HTML]{99BB99}4.5

@@

New engine version -- \texttt{E$_2$} & \cellcolor[HTML]{99BB99}1

@@

                                     & \cellcolor[HTML]{99BB99}1

@@

                                     & \cellcolor[HTML]{99BB99}1\\

@@

                                     & \cellcolor[HTML]{99BB99}3\\
New infrastructure -- \texttt{E$_4$} & \cellcolor[HTML]{99E899}3
                                     & \cellcolor[HTML]{99E899}3

@@

                                     & \cellcolor[HTML]{99E899}3
                                     & \cellcolor[HTML]{99BB99}5
                                     & \cellcolor[HTML]{99E899}3\\
  \textbf{Total} (difficulty to extend) & \cellcolor[HTML]{99E099}\textbf{9}
                                     & \cellcolor[HTML]{99E099}\textbf{9}

@@

                                     & \cellcolor[HTML]{99EF99}\textbf{8}
                                     & \cellcolor[HTML]{99BB99}\textbf{11.5}
                                     & \cellcolor[HTML]{99EF99}\textbf{8}\\

@@

Multiple engine instances -- \texttt{S$_1$}& \cellcolor[HTML]{99BB99}2
                                     & \cellcolor[HTML]{99DD99}1

@@

                                     & \cellcolor[HTML]{99DD99}1
                                     & \cellcolor[HTML]{99DD99}1\\
Distributed engines -- \texttt{S$_2$}& \cellcolor[HTML]{99BB99}1
                                     & \cellcolor[HTML]{99BB99}1
                                     & \cellcolor[HTML]{99BB99}1
                                     & \cellcolor[HTML]{99BB99}1

@@

\textbf{Total} (scalability issues)  & \cellcolor[HTML]{99BB99}\textbf{3}
                                     & \cellcolor[HTML]{99DD99}\textbf{2}
                                     & \cellcolor[HTML]{99DD99}\textbf{2}

@@

                                     & \cellcolor[HTML]{99DD99}\textbf{2}
                                     & \cellcolor[HTML]{99DD99}\textbf{2}\\

@@

  Meta-workflow  -- \texttt{O$_1$}    & \cellcolor[HTML]{99BB99}1
                                     & \cellcolor[HTML]{99BB99}1
                                     & \cellcolor[HTML]{99BB99}1
                                     & \cellcolor[HTML]{99BB99}1

@@

  \textbf{Total} (missing features) & \cellcolor[HTML]{99DD99}\textbf{1}
                                     & \cellcolor[HTML]{99DD99}\textbf{1}
                                     & \cellcolor[HTML]{99BB99}\textbf{2}
                                     & \cellcolor[HTML]{99DD99}\textbf{1}
                                     & \cellcolor[HTML]{99DD99}\textbf{1}

@@

\caption{Architecture evaluation. Lower values (brighter colors) indicate better performance. On each row, metric values are
  normalized between 0 (best value) and 1 (worst value) to determine the
  color of the corresponding table cell. The normalized metric value $m'$ is
  defined as
  $\frac{m-m_{\mathrm{min}}}{m_{\mathrm{min}}-m_{\mathrm{max}}}$ where
  $m$ is the initial metric value, $m_{\mathrm{min}}$ and $m_{\mathrm{max}}$
  are the minimal and maximal values among all architectures. The RGB hexadecimal color code of the cell
  is \texttt{\#99XX99}, where X=F-4m'. \todo{Use 6. Round to the nearest integer.}}
\label{table:evaluation}
\end{table*}

@@

Table~\ref{table:overall} provides an overall comparison between
architectures, based on the metrics in Table~\ref{table:evaluation}.
Overall, sub-tasking, and workflow import (with service invocation)
perform a bit better than tight integration, service invocation and
pool. Nested workflows stands a bit behind for the reasons mentioned
previously.
\begin{table*}
\centering
\begin{tabular}{rcccccc}
                                    & \textbf{Tight}
                                    & \textbf{Service}
                                    & \textbf{Sub-task}
                                    & \textbf{Pool}
                                    & \textbf{Nested}
                                    & \textbf{Import} \\
  Integration effort (normalized total) &
                                    \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99EF99}{0.22}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99E099}{0.44}
                                    & \cellcolor[HTML]{99BB99}{1.00}
                                      & \cellcolor[HTML]{99E899}{0.33}\\
Robustness (normalized total) &
                                \cellcolor[HTML]{99F599}{0.14}
                                    & \cellcolor[HTML]{99E199}{0.43}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99CE99}{0.71}
                                    & \cellcolor[HTML]{99BB99}{1.00}
                                    & \cellcolor[HTML]{99E199}{0.43}\\
  Extensibility (normalized total)  & \cellcolor[HTML]{99E099}{0.44}
                                     & \cellcolor[HTML]{99E099}{0.44}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99EF99}{0.22}
                                     & \cellcolor[HTML]{99BB99}{1.00}
                                     & \cellcolor[HTML]{99EF99}{0.22}\\
Scalability (normalized total)  & \cellcolor[HTML]{99BB99}{1.00}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}\\
Specific features (normalized total) & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99BB99}{1.00}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}\\
                                    & \cellcolor[HTML]{99EE99}\textbf{2.1}
                                    & \cellcolor[HTML]{99EE99}\textbf{2.1}
                                    & \cellcolor[HTML]{99FF99}\textbf{1.5}
                                    & \cellcolor[HTML]{99F499}\textbf{1.9}
                                    & \cellcolor[HTML]{99BB99}\textbf{4.0}
                                    & \cellcolor[HTML]{99FF99}\textbf{1.5}\\
\end{tabular}
\caption{Overall evaluation. Brighter colors and lower scores indicate better performance. Scores
  are obtained by summing the normalized total scores ($m'$ values) of
  each criterion in Table~\ref{table:evaluation} and the colors are obtained by normalizing these scores
  as done in Table~\ref{table:evaluation}. }
\label{table:overall}
\end{table*}

>>>>

\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\newcommand{\todo}[2]{\pdfmargincomment[color=red,author=#1,open=true]{#2}}
\newcommand{\note}[2]{\pdfmargincomment[color=yellow,author=#1,open=true]{#2}}
\newcommand{\closednote}[4]{\pdfmargincomment[color=gray,author=#1-#3,open=true]{#1: #2 \textCR \textCR #3: #4}}

@@

\begin{figure*}
\centering
\hspace*{0.2\columnwidth}
\subfloat[Tight integration]{
\def\svgwidth{0.6\columnwidth}
\input{figures/tight.pdf_tex}
\label{archi:tight}
}
\hfill
\subfloat[Service invocation]{
\def\svgwidth{0.6\columnwidth}
\input{figures/service.pdf_tex}
\label{archi:service}
\hspace*{0.2\columnwidth}
}\\
\hspace*{0.2\columnwidth}
\subfloat[Sub-tasking]{
\def\svgwidth{0.6\columnwidth}
\input{figures/sub-task.pdf_tex}
\label{archi:sub-task}
}
\hfill
\subfloat[Pool]{
\def\svgwidth{0.6\columnwidth}
\input{figures/agent.pdf_tex}
\label{archi:agent}
\hspace*{0.2\columnwidth}
}\\
\subfloat[Nested workflows. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-1.pdf_tex}
\def\svgwidth{0.9\columnwidth}
\input{figures/nested-2.pdf_tex}
\label{archi:nested}
}\\
\subfloat[Workflow import. Left: abstract model. Right: instantiation with service invocation.]{
\def\svgwidth{0.5\columnwidth}
\input{figures/import-1.pdf_tex}
\hfill
\def\svgwidth{0.5\columnwidth}
\input{figures/import-2.pdf_tex}
\label{archi:import}
}
\caption{Architectures}
\label{fig:architectures}
\end{figure*}
\begin{table*}
\centering
\footnotesize
\rowcolors{1}{white}{gray!25}
\begin{tabular}{ll}
  \textbf{Architecture} & \textbf{Systems} \\
  \hline
  Tight & \pbox{1.5\columnwidth}{
          Catania Science Gateway Framework~\cite{Ardizzone2012},
          Distributed application runtime environment (DARE~\cite{maddineni2012distributed}),
          DECIDE~\cite{ardizzone2012decide}$^{c,n}$, LONI Pipeline Environment$^n$~\cite{dinov2009efficient}
          }
  \\
  Service & \pbox{1.5\columnwidth}{
            Apache Airvata~\cite{marru2011apache}, e-BioInfra~\cite{shahand2015data}$^{w,n}$, HubZero with Pegasus~\cite{CPE:CPE3257}, MoSGrid~\cite{krüger2014mosgrid}$^w$, System in~\cite{wu2010accelerating}, Vine Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual Imaging Platform~\cite{GLAT-13}$^n$, WS-PGRADE/gUSE framework~\cite{Kacsuk2012},
            Science gateways in ~\cite{kacsuk2014science}$^w$
            } \\
  Sub-task & CBRAIN and PSOM~\cite{GLAT-16}$^n$, CBRAIN and FSL$^n$\\
  Pool & SHIWA pool~\cite{ROGE-13}\\
  Nested & \pbox{1.5\columnwidth}{SHIWA Simulation Platform (Coarse-Grained Interoperability~\cite{terstyanszky2014enabling})$^w$, HubZero with Pegasus (via hierarchical workflows)~\cite{Deelman201517} \todo{Tristan}{Add others}
  }\\
  Import & SHIWA Simulation Platform (Fine-Grained Interoperability)~\cite{plankensteiner-prodan-etal:2013}$^w$
\end{tabular}
\caption{Classification of science gateways based on the architecture used to integrate workflow engines. $^c$: based on the Catania Science Gateway Framework. $^w$: based on WS-PGRADE/gUSE. $^n$: used for neuroimaging.}
\label{table:system-classification}
\end{table*}

@@

\todo{Tristan}{Add description of a real system}

\todo{Tristan}{Refer to ``From the desktop to the grid: scalable bioinformatics via workflow conversion Luis de la GarzaEmail author, Johannes Veit, Andras Szolek, Marc Röttig, Stephan Aiche, Sandra Gesing, Knut Reinert and Oliver Kohlbacher''}

@@

                                     & \cellcolor[HTML]{99DD99}3

@@

                                     & \cellcolor[HTML]{99BB99}4
                                     & \cellcolor[HTML]{999999}5
                                     & \cellcolor[HTML]{99DD99}3\\

@@

                                     & \cellcolor[HTML]{99EE99}6

@@

                                     & \cellcolor[HTML]{99DD99}7
                                     & \cellcolor[HTML]{999999}11
                                     & \cellcolor[HTML]{99DD99}7\\

@@

                                     & \cellcolor[HTML]{99E899}\textbf{9}

@@

                                     & \cellcolor[HTML]{99D199}\textbf{11}
                                     & \cellcolor[HTML]{999999}\textbf{16}
                                     & \cellcolor[HTML]{99DD99}\textbf{10}\\

@@

                                     & \cellcolor[HTML]{99CC99}1

@@

                                     & \cellcolor[HTML]{999999}2
                                     & \cellcolor[HTML]{999999}2
                                     & \cellcolor[HTML]{99CC99}1\\
  Specific interactions -- \texttt{R$_2$} & \cellcolor[HTML]{99EA99}2
                                     & \cellcolor[HTML]{99D699}3

@@

                                     & \cellcolor[HTML]{99C199}4
                                     & \cellcolor[HTML]{999999}6
                                     & \cellcolor[HTML]{99D699}3\\
  \textbf{Total} (execution software pieces)& \cellcolor[HTML]{99F099}\textbf{2}
                                     & \cellcolor[HTML]{99D399}\textbf{4}

@@

                                     & \cellcolor[HTML]{99B699}\textbf{6}
                                     & \cellcolor[HTML]{999999}\textbf{8}
                                     & \cellcolor[HTML]{99D399}\textbf{4}\\

@@

  New engine type -- \texttt{E$_1$}  & \cellcolor[HTML]{99C499}3
                                     & \cellcolor[HTML]{99A799}4
                                     & \cellcolor[HTML]{99E199}2
                                     & \cellcolor[HTML]{99C499}3
                                     & \cellcolor[HTML]{999999}4.5

@@

New engine version -- \texttt{E$_2$} & \cellcolor[HTML]{999999}1

@@

                                     & \cellcolor[HTML]{999999}1

@@

                                     & \cellcolor[HTML]{999999}1\\

@@

                                     & \cellcolor[HTML]{999999}3\\
New infrastructure -- \texttt{E$_4$} & \cellcolor[HTML]{99DD99}3
                                     & \cellcolor[HTML]{99DD99}3

@@

                                     & \cellcolor[HTML]{99DD99}3
                                     & \cellcolor[HTML]{999999}5
                                     & \cellcolor[HTML]{99DD99}3\\
  \textbf{Total} (difficulty to extend) & \cellcolor[HTML]{99D199}\textbf{9}
                                     & \cellcolor[HTML]{99D199}\textbf{9}

@@

                                     & \cellcolor[HTML]{99E899}\textbf{8}
                                     & \cellcolor[HTML]{999999}\textbf{11.5}
                                     & \cellcolor[HTML]{99E899}\textbf{8}\\

@@

Multiple engine instances -- \texttt{S$_1$}& \cellcolor[HTML]{999999}2
                                     & \cellcolor[HTML]{99CC99}1

@@

                                     & \cellcolor[HTML]{99CC99}1
                                     & \cellcolor[HTML]{99CC99}1\\
Distributed engines -- \texttt{S$_2$}& \cellcolor[HTML]{999999}1
                                     & \cellcolor[HTML]{999999}1
                                     & \cellcolor[HTML]{999999}1
                                     & \cellcolor[HTML]{999999}1

@@

\textbf{Total} (scalability issues)  & \cellcolor[HTML]{999999}\textbf{3}
                                     & \cellcolor[HTML]{99CC99}\textbf{2}
                                     & \cellcolor[HTML]{99CC99}\textbf{2}

@@

                                     & \cellcolor[HTML]{99CC99}\textbf{2}
                                     & \cellcolor[HTML]{99CC99}\textbf{2}\\

@@

  Meta-workflow  -- \texttt{O$_1$}    & \cellcolor[HTML]{999999}1
                                     & \cellcolor[HTML]{999999}1
                                     & \cellcolor[HTML]{999999}1
                                     & \cellcolor[HTML]{999999}1

@@

  \textbf{Total} (missing features) & \cellcolor[HTML]{99CC99}\textbf{1}
                                     & \cellcolor[HTML]{99CC99}\textbf{1}
                                     & \cellcolor[HTML]{999999}\textbf{2}
                                     & \cellcolor[HTML]{99CC99}\textbf{1}
                                     & \cellcolor[HTML]{99CC99}\textbf{1}

@@

\caption{Architecture evaluation. Lower values (brighter colors) indicate better performance. On each row, metric values are
  normalized between 0 (best value) and 1 (worst value) to determine the
  color of the corresponding table cell. The normalized metric value $m'$ is
  defined as
  $\frac{m-m_{\mathrm{min}}}{m_{\mathrm{min}}-m_{\mathrm{max}}}$ where
  $m$ is the initial metric value, $m_{\mathrm{min}}$ and $m_{\mathrm{max}}$
  are the minimal and maximal values among all architectures. The RGB hexadecimal color code of the cell
  is \texttt{\#99XX99}, where X=F-4m'. \closednote{Tristan}{Use 6. Round to the nearest integer.}{Tristan}{Fixed.}}
\label{table:evaluation}
\end{table*}

@@

Table~\ref{table:overall} provides an overall comparison between
architectures, based on the metrics in Table~\ref{table:evaluation}.
Overall, sub-tasking, and workflow import (with service invocation)
perform a bit better than tight integration, service invocation and
pool. Nested workflows stands a bit behind for the reasons mentioned
previously.
\begin{table*}
\centering
\begin{tabular}{rcccccc}
                                    & \textbf{Tight}
                                    & \textbf{Service}
                                    & \textbf{Sub-task}
                                    & \textbf{Pool}
                                    & \textbf{Nested}
                                    & \textbf{Import} \\
  Integration effort (normalized total) &
                                    \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99E899}{0.22}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99D199}{0.44}
                                    & \cellcolor[HTML]{999999}{1.00}
                                      & \cellcolor[HTML]{99DD99}{0.33}\\
Robustness (normalized total) &
                                \cellcolor[HTML]{99F099}{0.14}
                                    & \cellcolor[HTML]{99D399}{0.43}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99B699}{0.71}
                                    & \cellcolor[HTML]{999999}{1.00}
                                    & \cellcolor[HTML]{99D399}{0.43}\\
  Extensibility (normalized total)  & \cellcolor[HTML]{99D199}{0.44}
                                     & \cellcolor[HTML]{99D199}{0.44}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99E899}{0.22}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99E899}{0.22}\\
Scalability (normalized total)  & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}\\
Specific features (normalized total) & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{999999}{1.00}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99CC99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.00}\\
                                    & \cellcolor[HTML]{99E699}\textbf{2.1}
                                    & \cellcolor[HTML]{99E699}\textbf{2.1}
                                    & \cellcolor[HTML]{99FE99}\textbf{1.5}
                                    & \cellcolor[HTML]{99EE99}\textbf{1.9}
                                    & \cellcolor[HTML]{999999}\textbf{4.0}
                                    & \cellcolor[HTML]{99FF99}\textbf{1.5}\\
\end{tabular}
\caption{Overall evaluation. Brighter colors and lower scores indicate better performance. Scores
  are obtained by summing the normalized total scores ($m'$ values) of
  each criterion in Table~\ref{table:evaluation} and the colors are obtained by normalizing these scores
  as done in Table~\ref{table:evaluation}. }
\label{table:overall}
\end{table*}
